---
title: "Plot of mtcars Data"
author: "Justin Z"
date: "June 5, 2019"
output: ioslides_presentation
---


```{r setup, include = FALSE}

knitr::opts_chunk$set(echo = FALSE)

```


## Overview

This report is for the week 3 peer-graded project in the Developing Data
Products course from Johns Hopkins University within the Data Science
Specialization on Coursera. The instructions say to create a web page using R
Markdown that features a plot created with `plotly`.

To meet the objective a 3D plot of the `mtcars` data was created. This report
page is hosted by GitHub Pages, and the repo for this project is [here][1]

[1]: xxxxx  "GitHub repo"


## Part 1) Loading and Processing the Data

In the code chunk below the required packages are loaded and the raw data is
loaded in. The data are then processed to prepare for plotting.

```{r loading, message = FALSE}

library(datasets)  # For the mtcars data
library(tidyverse)
library(plotly)

# Load data
data("mtcars")
mtcars <- as_tibble(mtcars, rownames = "vehicle")  # Put row names in a column

# Convert data types
mtcars <- mtcars %>%
  mutate(vs = as.factor(vs)) %>%
  mutate(am = as.factor(am)) %>%
  mutate(gear = as.factor(gear))

# The vs and am variables are coded with zeros and ones, but it will be easier
# to work with them by the names those values represent:
levels(mtcars$vs) <- c("V-shaped", "Straight")
levels(mtcars$am) <- c("Automatic", "Manual")

# Preview the data
mtcars

```


## Part 2) Generating the Map

In the next code chunk the data are placed into the map.

```{r plotting}

# Make the plot
plot_ly(x = mtcars$wt, y = mtcars$hp, z = mtcars$mpg, type = "scatter3d",
        mode = "markers", color = mtcars$am) %>%
  layout(scene = list(xaxis = list(title = "Vehicle Weight [klbs]"),
                      yaxis = list(title = "Horsepower [hp]"),
                      zaxis = list(title = "Fuel Economy [mpg]"))) %>%
  print()

```

