---
title: "Plot of mtcars Data"
subtitle: "Use left and right arrow keys to navigate slides"
author: "Justin Z"
date: "June 5, 2019"
output: ioslides_presentation
---


```{r setup, include = FALSE}

knitr::opts_chunk$set(echo = TRUE)

```


## Overview

This presentation is for the week 3 peer-graded project in the Developing Data
Products course from Johns Hopkins University within the Data Science
Specialization on Coursera. The instructions say to create a web page using R
Markdown that features a plot created with `plotly`.

To meet the objective a 3D plot of the `mtcars` data was created. This report
page is hosted by GitHub Pages, and the repo for this project is [here][1]

[1]: https://github.com/jtzingsheim1/mtcars-Presentation  "GitHub repo"


## Load and Process the Data

```{r load1, message = FALSE}

# Load packages
library(datasets); library(tidyverse); library(plotly)

# Load data
data("mtcars")
# Convert to tibble and put row names in a column
mtcars <- as_tibble(mtcars, rownames = "vehicle")  

# Convert data types
mtcars <- mtcars %>%
  mutate(vs = as.factor(vs)) %>%
  mutate(am = as.factor(am)) %>%
  mutate(gear = as.factor(gear))

# Convert factor values
levels(mtcars$vs) <- c("V-shaped", "Straight")
levels(mtcars$am) <- c("Automatic", "Manual")

```


## Preview the Data

```{r load2, echo = FALSE}

mtcars

```


## Create the Plot

```{r plot1}

# Make the plot
cars.plot <- plot_ly(x = mtcars$wt, y = mtcars$hp,
                    z = mtcars$mpg, type = "scatter3d",
                    mode = "markers", color = mtcars$am) %>%
  layout(scene = list(xaxis = list(title = "Vehicle Weight [klbs]"),
                      yaxis = list(title = "Horsepower [hp]"),
                      zaxis = list(title = "Fuel Economy [mpg]")))

```


## View the Plot

Click and drag to view different angles.

```{r plot2, echo = FALSE, warning = FALSE}

cars.plot

```


## Thank you!

